---
title: How many nets are needed to reach universal coverage - an update
author: Hannah Koenker
output:
  powerpoint_presentation:
    reference_doc: doc/th_template_2022.pptx
  # beamer_presentation:
  #   theme: "boxes"
  #   colortheme: "dove"
  #   fonttheme: "structurebold"
date: 21 Oct 2022
bibliography: quant_paper/quantbibfile.bib
biblio-style: quant_paper/model6-num-names
csl: https://www.zotero.org/styles/biomed-central
header-includes:
  - \usepackage{floatrow}
  - \usepackage{caption}
  - \floatsetup[figure]{capposition=top}
  - \floatplacement{figure}{H}
  - \usepackage{setspace}\doublespacing
  - \biboptions{sort&compress}
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE, include=FALSE}
######################
# Load Libraries
######################
# Load reading and basic libraries
library(rticles)
library(tidyverse)
library(haven)
library(readxl)
library(janitor)
library(viridis)
library(broom)
library(english)
library(magrittr)
library(lubridate)
library(countrycode)
library(data.table)
library(todor)

# Load map related libraries
library(sf)
library(tmap)
library(maptools)
library(maps)
library(spData)
library(distill)
library(geofacet)

# Load tables and plot libraries
library(flextable)
library(scales) # for heatmap in flextable
library(officer) # for setting color of vlines in flextable
library(gtsummary)
library(gt)
library(jtools)
library(kableExtra)
library(float)
library(ggstance)
library(knitr)
library(stringr)
library(stringi) # for removing accents from country names
library(ggpubr) # includes ggarrange and cowplot 
library(patchwork) # for insetting plots and nicer combos than ggarrange and cowplot, somehow
library(ggrepel)

# Load QR libraries
library(quantreg)
library(splines)

##### Might need to reinstall pandoc, if so, run this from Terminal. Takes a few minutes:
# brew install pandoc
# brew install pandoc-citeproc
# brew install pandoc-crossref
######

######################
# Set figure theme and colors
######################

theme_set(theme_classic())
# scale_colour_continuous <- function(...) scale_color_brewer(palette = "RdBu") 
# scale_colour_discrete   <- function(...) scale_color_brewer(palette = "Set2") # 
# scale_colour_binned     <- function(...) scale_color_fermenter(palette = "Set3")
# scale_fill_continuous <- function(...) scale_fill_brewer(palette = "RdBu") #
# scale_fill_discrete   <- function(...) scale_fill_brewer(palette = "Set3") # 
# scale_fill_binned     <- function(...) scale_fill_fermenter(palette = "Set3")

######################
# Knitr options
######################

knitr::opts_chunk$set(
  echo = FALSE, 
  message=FALSE, 
  warning=FALSE,
  tab.cap.style = "Caption") # set the table caption style so that Word can apply the right style! otherwise it's just normal.
## , dev="cairo_pdf")

options(knitr.kable.NA = "")

# knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
# knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="cairo_pdf", fig.width=7, fig.height=3.5)

# reason_palette <- c("net used"=rgb(102,194,165, maxColorValue=255), "objective" = rgb(141,160,203, maxColorValue=255), "subjective" = rgb(252,141,98, maxColorValue=255),  "risk perception" = rgb(231,138,195, maxColorValue=255),  "net attributes" = rgb(229,196,148, maxColorValue=255), "extra" = rgb(166,216,84, maxColorValue=255), "fears" = rgb(255,217,47, maxColorValue=255), "other"="lightgray")

```

# Introduction 

## Background (1)

- ITNs are not lasting as long as expected - most countries have an estimated retention time of less than 3 years [@10.1038/s41467-021-23707-7]. 

## Key Questions

1. what is the projected impact of the mismatch in campaign cycle and ITN retention in terms of overall ITN coverage? 

2. if mass campaigns every three years are insufficient due to ITNs lasting only 1-2 years, is switching to a two-year campaign cycle indicated, or are there alternative or supplemental ways to distribute ITNs to ensure high rates of ITN access are maintained over time? 

3. with what we know now about ITN retention and ITN distribution modalities, is "population divided by 1.8" still the correct quantification approach for mass campaigns for all countries? 

4. what would optimum ITN quantification look like for countries given their particular ITN retention times, aiming to sustain high levels of ITN access (the necessary, but not sufficient, precursor to ITN use)?

```{r oddhh}
odd <- read_dta("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/Caps/hh size and quant factors v5.dta") %>% 
  clean_names() %>% 
  select(percentodd)
```


## Background (2)

- The quantifier 1.8 was initially selected to account for the `r round(min(odd)*100, digits=1)`-`r round(max(odd)*100, digits=1)`% of households who have an odd number of household members, reflecting the need to round up in these cases [@Kilian:2010im]. 

- Kilian et al originally recommended dividing by 1.6, in order to accommodate distribution challenges including outdated census information and the need to preposition full bales of nets rather than precisely subdividing them. 

- In practice, WHO recommends "population divided by 1.8", and allows a buffer of up to 10% when the previous census is over 5 years old.

## Continuous distribution needs an "easy" quantification approach

- Quantification for continuous ITN distribution lacks a "population divided by X" quantifier. 

- Routine distribution to pregnant women and infants is already "easy", as these populations are a) relatively consistent at around 4% and 3% of the population, respectively, and b) attendance rates at antenatal care visits (ANC) and immunization visits (EPI) are generally well-monitored through HMIS. 

- Lack of an "easy" and serviceable quantification approach for CD has contributed in part to the limited scale-up of continuous distribution channels across malaria-endemic countries.

## Objective 

We will explore the above questions using an existing stock and flow model [@10.1186/s12936-022-04272-w] to project population ITN access for countries in sub-Saharan Africa over five different distribution scenarios, using estimated ITN retention times from Bertozzi-Villa et al [@10.1038/s41467-021-23707-7] and varying quantification approaches within each distribution scenario. Recommended quantifiers for each country are presented for each scenario and at different target levels of population ITN access.

# Methods

## Projections of future coverage

- Each country was assigned an indicative population of 10 million people in the database, starting in 2020, and an annual population growth rate of 3%, as the model outputs are adjusted for population and thus do not require specific population estimates.

## Scenarios

```{r table1, tab.cap = "Distribution Scenarios and their ITN inputs", fig.width=10}
scentable <- read_excel("data/scenario_table_text.xlsx", sheet = "pop times")
ftscen <- flextable(scentable) %>% 
  fontsize(size=10, part="all") %>% 
  set_table_properties(layout = "autofit") %>% 
  theme_vanilla
plot(ftscen)

## Pull the total number of scenarios/iterations:
totalscenarios <- scentable %>% 
  select(`Number of different iterations per scenario`) %>% 
  slice_max(`Number of different iterations per scenario`) %>% 
  pull()
```

## Estimating ITN access from net distributions and population (1)


```{r dmmap}
ls <- read_excel("data/Copy of MAP ITN retention data.xlsx", sheet="Sheet1") %>%
  clean_names() %>%
  drop_na(country) %>%
  rename(lifespan=median_retention_years) %>%
  separate(x95_percent_ci, into = c("lb", "ub"),
           sep = "\\s*(–|-)\\s*", convert = TRUE)


levels <- ls$country[ls$type=='MAP'][rev(order(ls$lifespan[ls$type=='MAP']))]
ls$country_ord <- factor(ls$country, levels = levels)

# save a small version of retention times for joining into results tables:
rettimes <- ls %>% 
  filter(type=="MAP") %>% 
  mutate(name=case_when(country=="Burkina" ~ "Burkina Faso",
                        # country=="Cote d'Ivoire" ~ "Côte d'Ivoire",
                        country=="Congo (Republic of)" ~ "Rep. Congo",
                        TRUE~as.character(country))) %>% 
  dplyr::select(-type, -country, -lb, -ub, -site, -both, -country_ord) %>% 
  mutate(name=stri_trans_general(name,"Latin-ASCII")) %>% # remove o-hat from Cote d'Ivoire
mutate(iso_a2 = countrycode(name, origin = "country.name", destination = "iso2c"))

a2levels <- rettimes$iso_a2 # make a list of the isoa2 countries included in retention times for later

dmmap <- ls %>%
  ggplot() +
  geom_point(aes(
    y = lifespan,
    x = country_ord,
    color = type,
    # alpha = both,
    shape = type
  ),
  alpha=0.8) +
  geom_linerange(aes(
    x = country_ord,
    ymin = lb,
    ymax = ub,
    color = type
    # alpha = both
  ),
  alpha=0.8) +
  theme_classic() +
  scale_alpha_continuous(range = c(0.25, 1), guide = "none") +
  scale_color_hue(
    # palette="Dark2",
    name = "Study Type", 
    labels = c("DM", "MAP")) +
  scale_shape_manual(
    name = "Study Type",
    labels = c("DM", "MAP"),
    values = c(19, 17)
  ) + # if guide=="none" here, shape won't appear correctly in legend
  theme(legend.position="right",
        text = element_text(size = 9),
        axis.title.y = element_text(size=8),
        axis.text.x = element_text(
    angle = 45,
    vjust = 0.9,
    hjust = 1,
    size = 7
  )) +
  labs(x = "",
       y = "Retention / median lifespan (years)")

# dmmap
# ggsave("MAP_vs_DM_lifespans.png")

```

```{r dmcurves}
### Graphing Stata Decay Curves in GGPLOT ####

# tz <- read_dta("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/Decay Curves/tz_decay_only.dta")
curves <- read_dta("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/Decay Curves/curves_only.dta") %>% 
  filter(lifespan<5.5)

decay <- ggplot() +
  geom_line(
    data = curves,
    aes(
      x = tdist,
      y = percsurv,
      color = as.factor(lifespan),
      linetype = as.factor(lifespan)
    ),
    alpha = 0.4
  ) +
  # geom_ribbon(
  #   data = tz,
  #   aes(x = tdist, ymin = lower, ymax = upper, fill="95% CI"),
  #   # fill = "lightgrey",
  #   alpha = 0.7
  # ) +
  # geom_line(data = tz, aes(x = tdist, y = percsurv), color = "orange") +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank()
  ) +
  # scale_fill_manual(name="Tanzania \n estimate", values="lightgrey") +
  scale_color_manual(
    name = "Median \nLifespan \n(years)",
    values = c(
      "dodgerblue",
      "dodgerblue",
      "red",
      "red",
      "seagreen",
      "seagreen",
      "darkorchid",
      "darkorchid",
      "pink"
    )
  ) +
  scale_linetype_manual(name = "Median \nLifespan \n(years)", values = c(1, 2, 1, 2, 1, 2, 1, 2, 1)) +
  scale_x_continuous(breaks=seq(0,9,1)) +
  theme(legend.position="right",
        text = element_text(size = 9)) +
  labs(
    y = "Percent of nets surviving",
    x = "Years since distribution",
    # title = "Net decay curves for \n varying median lifespans",
    color = "",
    fill=""
  )

# decay

# ggsave("decay_npc.png", width=8, height=5, units="in")

```

```{r npcaccess}
## Read in the regional level hhsize, access, npc data; from last run. Note that the resulting FIT is not necessarily the same as whatever was last
## run in the Stata do files.


Ddta <- read_dta("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/Analysis ITN Indicators compiled/regional_ITN_indicators.dta") 


D <- with(Ddta, data.frame(y = access_merg, x = itnpers, z = meanhh))

A <- as.matrix(D)
B <- as.data.frame(A)

taus <- 1:3/4 # make list of 0.25, .5, .75 for confidence bounds
xx <- seq(min(B[,2]), max(B[,2]),length=100) # make list of values .01-0.99
G <- matrix(0,length(xx),length(taus))
for(i in 1:length(taus)){
  f <- rqss(y ~ qss(x, constraint = "I", lambda = .5), tau = taus[i], data = B)
  G[,i] <- predict(f, newdata = list(x = xx))
}

#### 
## Make some subsets of the data by hh size groupings that we felt were worthwhile
## keep the 4 highest npc/access pairs available for all datasets

highest <- B %>% 
  filter(x>.80)

small <- B %>% 
  filter(z<4) %>% 
  bind_rows(highest) %>% 
  arrange(x)
med1  <- B %>% 
  filter(z>=4 & z<5) 
med2  <- B %>% 
  filter(z>=5 & z<6) 
large <- B %>% 
  filter(z>=6) %>% 
  bind_rows(highest) %>% 
  arrange(x)

taus <- 1:3/4 # make list of 0.25, .5, .75 for confidence bounds

## Small hh size countries:
xs <- seq(min(small[,2]), max(small[,2]),length=100) # make list of values .01-0.99
S1 <- matrix(0,length(xs),length(taus))
for(i in 1:length(taus)){
  f <- rqss(y ~ qss(x, constraint = "I", lambda = .5), tau = taus[i], data = small)
  S1[,i] <- predict(f, newdata = list(x = xs))
}

## Medium hh size countries
xm1 <- seq(min(med1[,2]), max(med1[,2]),length=100) # make list of values .01-0.99
S2 <- matrix(0,length(xm1),length(taus))
for(i in 1:length(taus)){
  f <- rqss(y ~ qss(x, constraint = "I", lambda = .5), tau = taus[i], data = med1)
  S2[,i] <- predict(f, newdata = list(x = xm1))
}

## Medium2 hh size countries
xm2 <- seq(min(med2[,2]), max(med2[,2]),length=100) # make list of values .01-0.99
S3 <- matrix(0,length(xm2),length(taus))
for(i in 1:length(taus)){
  f <- rqss(y ~ qss(x, constraint = "I", lambda = .5), tau = taus[i], data = med2)
  S3[,i] <- predict(f, newdata = list(x = xm2))
}

## Large hh size countries
  xl <- seq(min(large[,2]), max(large[,2]),length=100) # make list of values .01-0.99
  S4 <- matrix(0,length(xl),length(taus))
  for(i in 1:length(taus)){
    f <- rqss(y ~ qss(x, constraint = "I", lambda = .5), tau = taus[i], data = large)
    S4[,i] <- predict(f, newdata = list(x = xl))
  }

# Save as dataframes and create npc variable (will be divided by 100 and rounded later in Stata)
S1 <- as.data.frame(S1) %>%
  mutate(hhsize=0,
         npc=row_number()) # small
S2 <- as.data.frame(S2) %>%  
  mutate(hhsize=1,
         npc=row_number()) # med1
S3 <- as.data.frame(S3) %>% 
  mutate(hhsize=2,
         npc=row_number()) # med2
S4 <- as.data.frame(S4) %>% 
  mutate(hhsize=3,
         npc=row_number()) # large

fithhsize <- S1 %>% 
  bind_rows(S2, S3, S4)

write.csv(fithhsize, "data/itnpers_into_access_transformation_hh.csv")



### Make G into a dataframe and rename the variables for ggplot later: 
gg <- as.data.frame(G) %>% 
  mutate(access=V2,
         lb=V1,
         ub=V3) %>% 
  arrange(access) %>% 
  mutate(npc=1:n()/100) %>% # make a new variable which is the row count and also NPC because Dad did not include this!
  mutate(delta=ub-lb)

npc <- ggplot() +
  geom_point(data=B, aes(x,y), alpha=0.5, shape=1, size=0.5) +
  geom_line(data=gg, aes(npc, access)) +
  geom_line(data=gg, aes(npc, lb, color="50% confidence bounds")) +
  geom_line(data=gg, aes(npc, ub, color="50% confidence bounds")) +
  theme_minimal() +
  theme(legend.position="bottom",
        text = element_text(size = 9)) +
  labs(x="ITNs per capita (NPC)",
       y="% ITN Access",
       color="")

npchh <- fithhsize %>% 
  mutate(npcd=npc/100) %>% 
  ggplot() +
  geom_point(data=B, aes(x, y), color="lightgray", alpha=0.2) +
  geom_line(aes(npcd, V2, color=as.factor(hhsize))) +
  geom_ribbon(aes(npcd, ymin=V1, ymax=V3, fill=as.factor(hhsize)), alpha=0.2) +
  labs(x="ITNs per capita",
       y="Estimated ITN access",
       color="Mean\nhousehold\nsize")+
  scale_color_hue(
    # palette="Dark2",
    labels=c("<4","4-4.9","5-5.9","≥6")) +
  theme(legend.position="right",
        text = element_text(size = 9)) +
  guides(fill="none")
```

```{r ret-decay-fig, fig.width = 10, fig.cap = "A) ITN retention times and median lifespans estimated from durability monitoring studies B) Smooth-compact loss function for net decay C) nonparametric conditional quartile function for ITN access as a function of NPC"}

dmmap / (decay | npchh) + 
  plot_annotation(tag_levels = 'A')
```

:::

For each year, the stock and flow model used a country-specific estimated median lifespan from Malaria Atlas Project (MAP) estimates published in Bertozzi-Villa et al [@10.1038/s41467-021-23707-7], shown in blue in Fig. \@ref(fig:ret-decay-fig)A, to decay each crop of distributed nets annually. Fig. \@ref(fig:ret-decay-fig)A also presents estimated median lifespans from ITN durability monitoring (DM) activities gathered from www.pmi.gov and published literature [@Abilio:2020fl; @Kilian:2020dj; @Mansiangi:2020cv; @Haji:2020de; @Obi:2020eza; @Kilian:2015hk; @10.1371/journal.pmed.1003248; @Randriamaherijaona:2017fo]. The net decay functions rely on smooth-compact loss function developed by Nakul Chitnis and described in Koenker et al and Bhatt et al [@Koenker:2013ed; @Bhatt:2015gn; @10.1186/s12936-022-04272-w], and are shown in Fig. \@ref(fig:ret-decay-fig)B.

:::

```{r afpop}
## Extract Africa population data from giant World Bank file - but Eritrea is missing ## https://datacatalog.worldbank.org/search/dataset/0037655 

# df <- as.data.frame(read_csv("data/WB_Population_Estimates_CSV/Population-EstimatesData.csv")) %>% 
#   clean_names() %>% 
#   select(country_name, country_code, indicator_name, indicator_code, x2020, x2021, x2022, x2023, x2024, x2025, x2026, x2027, x2028, x2029, x2030, x2031, x2032, x2033, x2034, x2035, x2036, x2037) %>% 
#   filter(indicator_name=="Population, total") %>% 
#   mutate(ccode=country_code) %>% 
  # drop_na(x2025) 
# afpop <- df %>% 
#   mutate(iso_a2=countrycode(country_code, origin="iso3c", destination="iso2c")) %>% 
#   filter(iso_a2 %in% a2levels)
# 
# rm(df)

## Extract Africa population data from UN WPP 2022 Demographic Indicators Medium File (https://population.un.org/wpp/Download/Standard/CSV/)

afpop <- as.data.frame(read_csv("data/WPP2022_Demographic_Indicators_Medium.csv")) %>% 
  clean_names() %>% 
  select(iso2_code, iso3_code, location, t_population1july, time) %>% 
  mutate(t_population1july=t_population1july*1000) %>% 
  rename(pop=t_population1july,
         year=time,
         iso_a2=iso2_code,
         country_code=iso3_code,
         country_name=location) %>% 
  filter(year>2019 & year<2041) %>% 
  filter(iso_a2 %in% a2levels) %>% 
  pivot_wider(names_from=year, names_prefix="x", values_from=pop)


```

## Estimating ITN access from net distributions and population (2)

- The total net crop (consisting of all surviving nets from various channels to date) was summed for each year and country. This was then divided by the population projected to calculate nets-per-capita (NPC). To estimate ITN access from NPC, a nonparametric conditional quartile function for ITN access as a function of NPC was estimated from `r length(unique(Ddta$dataset))` Demographic and Health Surveys (DHS) and malaria indicator surveys (MIS). 

- Confidence intervals for both estimated median lifespan and the function of ITN access vs NPC were used to generate an overall confidence interval around the estimate of ITN access.

- Recommended quantifiers were obtained by identifying the scenario that provided the greatest number of years of ITN access at or above the target level; if multiple scenarios provided the same number of years, the scenario requiring the fewest nets was selected.


# Results
```{r readmins}
s2min <- read_dta("data/s2_min_npp.dta") %>% 
  clean_names()
s2mean <- read_dta("data/s2_mean_npp.dta") %>% 
  clean_names()

s3min <- read_dta("data/s3_min_npp.dta") %>% 
  clean_names()
s3mean <- read_dta("data/s3_mean_npp.dta") %>% 
  clean_names()

s2max <- read_dta("data/s2_max_acc.dta") %>% 
  mutate(maxacc = round_half_up(maxacc, digits=0))

s4min <- read_dta("data/s4_min_acc.dta") %>% 
  clean_names() 

s5min <- read_dta("data/s5_min_acc.dta") %>% 
  clean_names() 

## Grab the low and high quantifiers for Scenario 2 for results inline code
s2_70_low <- s2min %>% 
  filter(target==70) %>% 
  top_n(1, -q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s2_70_high <- s2min %>% 
  filter(target==70) %>% 
  top_n(1, q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s2_80_low <- s2min %>% 
  filter(target==80) %>% 
  top_n(1, -q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s2_80_high <- s2min %>% 
  filter(target==80) %>% 
  top_n(1, q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s2_90_low <- s2min %>% 
  filter(target==90) %>% 
  top_n(1, -q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s2_90_high <- s2min %>% 
  filter(target==90) %>% 
  top_n(1, q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

## Grab highs and low quantifiers from the Scenario 3 targets:
s3_70_low <- s3min %>% 
  filter(target==70) %>% 
  top_n(1, -q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name")) %>% 
  left_join(rettimes)

s3_70_high <- s3min %>% 
  filter(target==70) %>% 
  top_n(1, q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s3_80_low <- s3min %>% 
  filter(target==80) %>% 
  top_n(1, -q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s3_80_high <- s3min %>% 
  filter(target==80) %>% 
  top_n(1, q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s3_90_low <- s3min %>% 
  filter(target==90) %>% 
  top_n(1, -q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

s3_90_high <- s3min %>% 
  filter(target==90) %>% 
  top_n(1, q) %>% 
  mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name"))%>% 
  left_join(rettimes)

shortlist2 <- c("LR","GN","TZ","TG","CG","CM")
shortlist3 <- c("LBR","GIN","TZA","TGO","COG","CMR")
```



```{r grid}
geofacet_fname <- "data/geofacet_ssa.csv" # load geofaceting data for sub saharan africa
ssa_grid <- fread(geofacet_fname) # make it a grid for tiny maps in africa continent layout

s1title <- "3-year mass campaigns with ANC/EPI at "
s2title <- "ANC/EPI at 6% and annual school/community \ndistribution at "
s3title <- "3-year mass campaigns with ANC/EPI at 6% and \nbetween-campaign school/community distribution at "
s4title <- "3-year mass campaigns with ANC/EPI, \nat population / "
s5title <- "2-year mass campaigns with ANC/EPI, \nat population / "
```


```{r geofacet_function}
# read data in and plot
geofun <- function(scen, title) {
  # splot <- 
    read_dta(filename) %>%
    select(percpop, year, accrk, iso3, acclb_npclb, accub_npcub) %>%
    mutate(name = countrycode(iso3, origin = "iso3c", destination = "country.name")) %>%
    mutate(code = iso3) %>%
    ggplot(aes(x = year - 2000)) +
   geom_hline(yintercept = 80, size=0.25, linetype="solid", color = "red", alpha = 0.5) +
  geom_hline(yintercept = 90, size=0.25, linetype="solid", color = "red", alpha = 0.5) +
  # geom_line(aes(y = percpop, color = "percpop"), alpha = 0.5, size = 0.75) +
  geom_line(aes(y = accrk, color = "accrk"), alpha = 0.5, size = 0.75) +
    geom_ribbon(aes(ymin = acclb_npclb, ymax = accub_npcub),
                color = NA,
                alpha = 0.25) +
    scale_color_brewer(
      palette = "Dark2",
      labels = c("Predicted \nITN Access")
    ) +
    scale_x_continuous(breaks = seq(20, 35, 5),
                       labels = c("'20", "'25", "'30", "'35")) +
    theme_minimal() +
    facet_geo( ~ code, grid = ssa_grid, label = "code") +
    labs(title = paste(title, X, "% of the population"),
         x = "",
         y = "Percent",
         color = "") +
    theme(
      # legend.position="none",
      # axis.text.x = element_text(angle=45, hjust=1)
      # axis.text.x = element_blank(),
      axis.line = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text = element_text(size = 6),
      panel.grid.major.x = element_line(color = "darkgrey", size =
                                          0.25)
    ) +
    scale_alpha(guide = 'none') +
    scale_size(guide = 'none')
  # print(splot)
  # plotname <- paste("figs/scen_",scen,".pdf", sep = "")
  # ggsave(plotname)
}
```

## ITN access for Scenario 1 - status quo

```{r geo-facets-3ucc, warning = FALSE, message=FALSE, fig.width = 5, fig.cap = "ITN access estimated for 3-year mass campaign strategy, with ANC/EPI distribution at 6% of the population annually"}

s1 <- 106 ## set the scenario selected for inclusion in the paper

# create the path and filename from the scenario number
filename = paste("output/runs/", s1, ".dta", sep = "")
  
# extract the quantifier from scenario number (last two digits) to put into the titles
X <- s1-round(s1,digits=-2)
  
geofun(scen = s1, title = s1title)
```

## ITN access for Scenario 2 - full scale CD

```{r geo-facets-cd, warning = FALSE, message=FALSE, fig.width = 5, fig.cap = "Estimated ITN access with annual ANC/EPI at 6% and full continuous distribution strategy at 17% of the population in nets each year. Shaded areas indicate 95% confidence intervals accounting for both net retention times and ITN access as a function of nets-per-capita (NPC)"}

s2 <- 217 ## set the scenario selected for inclusion in the paper

# create the path and filename from the scenario number
filename = paste("output/runs/", s2, ".dta", sep = "")
  
# extract the quantifier from scenario number (last two digits) to put into the titles
X <- s2-round(s2,digits=-2)
  
geofun(scen = s2, title = s2title)

```

## ITN access for Scenario 3 - CD between campaigns

```{r geo-facets-cducc, warning = FALSE, message=FALSE, fig.width = 5, fig.cap = "Scenario 3 - three-year mass campaigns with ANC/EPI distribution at 6%, and between-campaign continuous distribution at 10%"}

s3 <- 310 ## set the scenario selected for inclusion in the paper

# create the path and filename from the scenario number
filename = paste("output/runs/", s3, ".dta", sep = "")
  
# extract the quantifier from scenario number (last two digits) to put into the titles
X <- s3-round(s3,digits=-2)
  
geofun(scen = s3, title = s3title)

```

The complete set of graphs for all `r totalscenarios` scenarios is included as Supplemental File 1.

## We are not distributing enough nets to maintain ITN access at 80%

- Given a target of 80% ITN access, the recommended quantification approaches for each scenario varied considerably across countries. 
- Adjustments in quantification for ANC-EPI distribution did not lead to large differences in ITN access in Scenario 1. 
- The key factors driving variation across countries within a given scenario were the estimated retention times for each country and the mean household size. 
- Recommended quantification approaches are summarized for the scenarios that include continuous distribution in Table \@ref(tab:table-min-quantifier), for 3-year mass campaigns in Table \@ref(tab:tabscen4), and for 2-year mass campaigns in Table \@ref(tab:tabscen5).



```{r Quantifier_Table}
t2 <- s2min %>% 
  pivot_wider(names_from = target, values_from = q) %>% 
  relocate(`70`, .before = `80`) %>% 
  relocate(`90`, .after = `80`) %>% 
#mutate(scenario = "s2")  
rename("s270" = `70`,
       "s280" = `80`,
        "s290" = `90`)

t3 <- s3min %>% 
  pivot_wider(names_from = target, values_from = q) %>% 
  relocate(`70`, .before = `80`) %>% 
  relocate(`90`, .after = `80`) %>% 
  #mutate(scenario = "s3") 
  rename("s370" = `70`,
       "s380" = `80`,
        "s390" = `90`)

# join tables
table_q_s2s3long <- t2 %>% 
  left_join(t3, by = "iso_a2") %>% 
  arrange(iso_a2) %>%
  left_join(rettimes) %>% 
  mutate(lifespan=round(lifespan, digits=1),
         iso3=countrycode(iso_a2, origin="iso2c", destination="iso3c")) %>% 
  dplyr::select(iso3, lifespan, s270, s280, s290, s370, s380, s390) %>% 
  arrange(lifespan)

table_q_s2s3short <- table_q_s2s3long %>% 
  filter(iso3 %in% shortlist3)

# export table to csv for use in file 06 School Suitability and for pulling into quant_paper.Rmd:
# write.csv(table_q_s2s3, "output/s2s3table.csv", row.names = FALSE)

```

## Quantification factors for continuous distribution strategies 

All scenarios assume that ANC and EPI delivery of ITNs is ongoing and provides nets to 6% of the population. However, quantifiers listed in the table represent only the continuous distribution channel, e.g. Liberia would require both ANC/EPI distribution as well as continuous distribution quantified using population x 28% to maintain ITN access at levels of 70%.

```{r table-min-quantifier, fig.width=7, tab.cap = "Recommended annual quantifiers for continuous distribution channels. "}

std_border = fp_border(color="gray") ## set the color of the border needed later down

tables2s3function <- function(df) {
  flextable(df) %>% 
   set_header_labels(
   iso3 = "Country Code",
   lifespan = "Retention time (years)",
             s270 = "70%",
             s280 = "80%",
             s290 = "90%",
             s370 = "70%",
             s380 = "80%",
             s390 = "90%"
  ) %>%
  add_header_row(colwidths = c(2, 6),
                 values = c("", "Targeted ITN access level:")) %>%
  add_header_row(
    colwidths = c(2,3,3),
    values = c("", "Scenario 2 (full continuous distribution strategy)", "Scenario 3 (continuous distribution between mass campaigns)")
  ) %>%
     add_header_row(
       colwidths = c(8),
       values=c("Minimum quantifier (population x X%, annually) to sustain ITN access at specified target level")
     ) %>% 
  fontsize(size = 9, part = "body") %>%
  fontsize(size=10, part="header") %>% 
  colformat_double(
    j=3:8,
    big.mark = ",",
    digits = 0,
    na_str = ""
  ) %>% 
  theme_vanilla %>%
  align(align = "center", part = "all") %>% 
  vline(j=5, border=std_border, part="all") %>% 
  vline(j=2, border=std_border, part="all") %>% 
  set_table_properties(width=.5)
} 

plot(tables2s3function(table_q_s2s3short))

```


```{r s45mindata}
s45colnames <- c("Cty","1.0","1.1","1.2","1.3","1.4","1.5","1.6","1.7","1.8","1.9","2.0")
examplecountry <- "GN" ## set the example country we want to use in the text here.

t4 <- read_dta("data/s4q.dta") %>% 
  rename(s4=best) %>% 
  mutate(s4=(s4-400)/10)
  
 t5 <- read_dta("data/s5q.dta") %>% 
  rename(s5=best) %>% 
  mutate(s5=(s5-500)/10)
 
 t4_18 <- s4min %>% 
   select(iso_a2, accrk418) %>% 
   filter(accrk418>=80) %>% 
   # mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name")) %>% 
   left_join(rettimes)
 
t4_16 <- s4min %>% 
   select(iso_a2, accrk416) %>% 
   filter(accrk416>=80) %>% 
   # mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name")) %>% 
   left_join(rettimes)

examplecty4 <- s4min %>% 
  filter(iso_a2==examplecountry) %>% 
  left_join(rettimes)

t5_18 <- s5min %>% 
   select(iso_a2, accrk518) %>% 
   filter(accrk518>=80) %>% 
   # mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name")) %>% 
   left_join(rettimes)
 
t5_16 <- s5min %>% 
   select(iso_a2, accrk516) %>% 
   filter(accrk516>=80) %>% 
   # mutate(country=countrycode(iso_a2, origin="iso2c", destination="country.name")) %>% 
   left_join(rettimes)
  
examplecty5 <- s5min %>% 
  filter(iso_a2==examplecountry) %>% 
  left_join(rettimes)

totcty <- s5min %>% 
  nrow()  ## grab the total number of countries in the analysis
```



```{r s4function-setup}

colourer <- col_numeric(
  palette = scales::col_numeric(palette = paletteer::paletteer_d(palette = "Redmonder::dPBIRdGn") %>% as.character(),
                                 domain = NULL),
  domain = c(0, 100))

white_border= fp_border(color="white", width=2) ## set the color of the border needed later down

s4tablefunction <- function(df) {
    flextable(df) %>%
  set_header_labels(
    iso3 = "Cty",
    lifespan = "Retention time (years)",
    # accrk405 = "0.5",
    # accrk406 = "0.6",
    # accrk407 = "0.7",
    # accrk408 = "0.8",
    # accrk409 = "0.9",
    accrk410 = "1.0",
    accrk411 = "1.1",
    accrk412 = "1.2",
    accrk413 = "1.3",
    accrk414 = "1.4",
    accrk415 = "1.5",
    accrk416 = "1.6",
    accrk417 = "1.7",
    accrk418 = "1.8",
    accrk419 = "1.9",
    accrk420 = "2.0"
  ) %>%
  add_header_row(colwidths = c(2, 11),
                 values = c("", "Population divided by:")) %>%
  add_header_row(
    colwidths = c(13),
    values = c("Lowest ITN access between 3-year campaigns for each quantifier")
  ) %>%
  fontsize(size = 9, part = "all") %>%
  colformat_double(
    j=3:13,
    big.mark = ",",
    digits = 0,
    na_str = ""
  ) %>%
  bg(
    bg = colourer,
    j = 3:13,
    part = "body") %>% 
  theme_vanilla %>% 
  align(align = "center", part = "header") %>% 
  vline(j = c(10,11), border=white_border, part="body") %>% 
  set_table_properties(layout="autofit", width=.7)
}

```

## Tailored quantification factors for 3-year campaigns 
```{r tabscen4, fig.width=10, tab.cap = "Lowest level of ITN access between 3-year campaigns at different population quantifiers. Green color reflects higher ITN access while red indicates lower ITN access reached between campaigns.  Routine ITN delivery to pregnant women and infants is assumed."}

s4minrtlong <- s4min %>% 
  left_join(rettimes) %>% 
  select(-name, -contains("accrk40")) %>% 
  mutate(lifespan=round(lifespan, digits=1),
         iso3=countrycode(iso_a2, origin="iso2c", destination="iso3c")) %>% 
  select(-iso_a2) %>% 
  select(iso3, lifespan, everything())

s4minrtshort <- s4minrtlong %>% 
  filter(iso3 %in% shortlist3) %>% 
  arrange(lifespan)

plot(s4tablefunction(s4minrtshort))
```




```{r s5tablefunction}
s5tablefunction <- function(df) {
  flextable(df) %>%
  set_header_labels(
    iso3 = "Cty",
    lifespan = "Retention time (years)",
    accrk510 = "1.0",
    accrk511 = "1.1",
    accrk512 = "1.2",
    accrk513 = "1.3",
    accrk514 = "1.4",
    accrk515 = "1.5",
    accrk516 = "1.6",
    accrk517 = "1.7",
    accrk518 = "1.8",
    accrk519 = "1.9",
    accrk520 = "2.0"
  ) %>%
  add_header_row(colwidths = c(2, 11),
                 values = c("", "Population divided by:")) %>%
  add_header_row(
    colwidths = c(13),
    values = c("Lowest ITN access between 2-year campaigns for each quantifier")
  ) %>%
  fontsize(size = 9, part = "all") %>%
  align(align = "center", part = "header") %>%
  colformat_double(
    j=3:13,
    big.mark = ",",
    digits = 0,
    na_str = ""
  ) %>%
  bg(
    bg = colourer,
    j=3:13,
    part = "body") %>% 
  theme_vanilla %>% 
  align(align = "center", part = "header") %>% 
  vline(j = c(10,11), border=white_border, part="body") %>% 
  set_table_properties(layout="autofit", width=.7)
}
```

## Tailored quantification factors for 2-year campaigns 

```{r tabscen5, fig.width=10, tab.cap = "Lowest level of ITN access between 2-year campaigns at different population quantifiers. Green color reflects higher ITN access while red indicates lower ITN access reached between campaigns. Values of 100 indicate excess nets in the system (for example Cameroon). Routine ITN delivery to pregnant women and infants is assumed."}

s5minrtlong <- s5min %>% 
  left_join(rettimes) %>% 
  select(-name, -contains("accrk50")) %>% 
  mutate(lifespan=round(lifespan, digits=1),
         iso3=countrycode(iso_a2, origin="iso2c", destination="iso3c")) %>%  
  select(-iso_a2) %>% 
  select(iso3, lifespan, everything())

s5minrtshort <- s5minrtlong %>% 
  filter(iso3 %in% shortlist3) %>% 
  arrange(lifespan)


plot(s5tablefunction(s5minrtshort))
```


## Recommended quantification factors for countries and scenarios

```{r reccs-data}

qt <- read.csv("output/s2s3table.csv") # this table is produced in the code further above and gets joined later on; don't drop columns here

qt80 <- qt %>% 
  select(iso_a2, s280, s380) # just keep the target=80 columns for Scen 2 & 3, for merging below


sumtable <- t4 %>% 
  right_join(t5) %>% 
  right_join(qt80) %>% 
  mutate(name = countrycode(iso_a2, origin = "iso2c", destination = "country.name")) %>% 
  arrange(iso_a2)

table80 <- sumtable %>% 
  select(name, s280, s380,s4, s5) %>% 
  rename(scenario_2 = s280,
         scenario_3 = s380,
         scenario_4=s4,
         scenario_5=s5) %>% 
  select(name, scenario_2, scenario_3, scenario_4, scenario_5)

table80rtlong <- table80 %>% 
  mutate(name=case_when(name=="Congo - Kinshasa" ~ "DRC",
                        name=="Congo - Brazzaville" ~ "Rep. Congo",
                        name=="Côte d'Ivoire" ~ "Cote d'Ivoire",
                        TRUE~as.character(name))) %>% 
  mutate(name=stri_trans_general(name,"Latin-ASCII")) %>% # remove o-hat from Cote d'Ivoire
right_join(rettimes) %>% 
  filter(iso_a2!="MM") %>% 
  mutate(lifespan=round(lifespan, digits=1),
         iso3=countrycode(iso_a2, origin="iso2c", destination="iso3c")) %>% 
  arrange(iso3, scenario_3) %>% 
  select(-iso_a2) %>% 
  select(iso3, lifespan, scenario_2, scenario_3, scenario_4, scenario_5)

table80rtshort <- table80rtlong %>% 
  filter(iso3 %in% shortlist3) %>% 
  arrange(lifespan)
  

```

```{r regionalschooldata}
## Reading in school quant sheets to calculate % of regions that could make school dist work 
## based on DHS data on % pop that are school-attending primary school students

# read in sheets

sheets_to_read <- excel_sheets("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/School Quant/schoolquant_v2.xlsx") ##Obtain the sheets in the workbook

# x <- c("National Results")

# sheets_to_read <- within(sheets_to_read, rm("National Results"))

list_with_sheets <- lapply(sheets_to_read,
                           function(i)read_excel("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/School Quant/schoolquant_v2.xlsx", sheet = i))

names(list_with_sheets) <- sheets_to_read ##Add names

x1 <- lapply(list_with_sheets,clean_names) ## apply the clean_names function to the full list
invisible(list2env(x1 ,.GlobalEnv)) ## This function should put all the dataframes within the list (x1) into the global environment. Make it 'invisible' otherwise it appears in the Markdown.

rm("National Results")
natl <-  read_excel("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/School Quant/schoolquant_v2.xlsx", sheet="National Results") %>% 
  clean_names() %>% 
  mutate(country=case_when(country=="Sierra" ~ "Sierra Leone",
                           country=="Burkina" ~ "Burkina Faso",
                           country=="Congo" ~ "Rep. Congo",
                           country=="Cote" ~ "Cote d'Ivoire",
                           country=="Sao" ~ "Sao Tome and Principe",
                           country=="Papua" ~ "Papua New Guinea",
                           country=="East" ~ "Timor Leste",
                           TRUE ~ as.character(country)
                           )) %>% 
  mutate(iso_a2=countrycode(country, origin="country.name", destination="iso2c"))
  
allsch <- x1 %>% reduce(bind_rows) %>% 
  drop_na(region) %>% 
  mutate(country=case_when(country=="Sierra" ~ "Sierra Leone",
                           country=="Burkina" ~ "Burkina Faso",
                           country=="Congo" ~ "Rep. Congo",
                           country=="Cote" ~ "Cote d'Ivoire",
                           country=="Sao" ~ "Sao Tome and Principe",
                           country=="Papua" ~ "Papua New Guinea",
                           country=="East" ~ "Timor Leste",
                           TRUE ~ as.character(country)
                           )) %>% 
  mutate(iso_a2=countrycode(country, origin="country.name", destination="iso2c"))

rm("AOHR71","BFHR62", "BJHR71", "BUHR61", "CIHR62", "CMHR71", "CDHR61","CGHR60", "GAHR60", "GHHR72", "GMHR81", "GNHR71", "GYHR51", "HTHR70", "KEHR71", "KHHR51", "KMHR61", "LBHR7A", "MDHR80", "MLHR7H", "MMHR71", "MRHR71", "MWHR7H", "MZHR62", "NGHR7A", "NIHR61", "NMHR61", "PGHR70", "RWHR81", "SLHR7A", "SNHR8A", "STHR50", "SZHR51","TDHR71", "TGHR61", "TLHR71", "TZHR7H", "UGHR7H", "ZMHR71", "ZWHR71")

## National Level School Results - not sure this code is needed
# now need to compare the % current primary students to the percent quantifier needed to maintain 80% ITN access.
schv2 <- read_excel("/Users/hannahkoenker/Dropbox/A DHS MIS Datasets/Analysis/School Quant/schoolquant_v2.xlsx") %>% 
  clean_names() %>% 
   # mutate(name = countrycode(iso3, origin = "iso3c", destination = "country.name")) %>%
  mutate(name_long = case_when(country == "DRC" ~ "Democratic Republic of the Congo",
                          country == "Congo" ~ "Rep. Congo",
                          country == "Cote" ~ "Côte d'Ivoire",
                          country == "Sierra" ~ "Sierra Leone",
                          country == "Sao" ~ "Sao Tome",
                          country == "Gambia" ~ "The Gambia",
                          country == "Swaziland" ~ "eSwatini",
                          country == "Burkina" ~ "Burkina Faso",
                          TRUE ~ as.character(country))) %>% 
  rename(feasible17 = full_scale_school_is_feasible,
         for17 = number_of_classes_needed_annually_for_full_scale_school_distribution_pop_5_8_or_17_percent_of_pop,
         percattending = percent_hh_with_child_attending_primary_school,
         currentprim = percent_population_that_are_current_primary_students,
         classes = number_classes_needed_for_between_campaign_school_distribution
  )
  
```

```{r recctable80, fig.width=10, tab.cap = "Summary of recommended quantifiers for scenarios, to maintain ITN access at or above 80%. The quantifiers are for only the continuous distribution channel or mass campaign; annual RCH distribution equivalent to 6% of the population is assumed in each scenario, but is not part of the listed quantifiers"}
## Join retention times to table80


recctablefunction <- function(df) {
  flextable(df) %>% 
  set_header_labels(iso3="Country",lifespan="Retention time (years)", scenario_2="Full-scale continuous + routine",scenario_3="Campaign + routine + continuous between campaigns",scenario_4="3-yearly campaigns",scenario_5="2-yearly campaigns") %>% 
  add_header_row(colwidths = c(2,2,2), values=c("","Continuous Distribution\nITNs = Population x X, annually","Mass Campaign\nITNs = Population / X")) %>% 
  # width(width=.2) %>% 
  fontsize(size=9, part="all") %>% 
    set_formatter( scenario_2 = function(x) sprintf( "%.0f%%", x*1 ),
                   scenario_3 = function(x) sprintf( "%.0f%%", x*1 )) %>% 
  theme_vanilla %>% 
    align(align = "center", part = "all") %>% 
  vline(j=c(2,4), border=std_border, part="header") %>% 
  # fit_to_width(max_width=6, inc = 1L, max_iter = 20, unit = "in") %>% 
    set_table_properties(layout="autofit", width=.7) %>%
  height(height=0.3, part="body") %>% 
  hrule(rule="exact", part="body")
}
plot(recctablefunction(table80rtshort))
```

## How many nets are needed under the recommended scenarios?

```{r totalnetsdf}
# Figure for Total Nets Needed in an 10 year timeframe (2022-2032) for different scenarios
tnets <- table80rtlong %>% 
  mutate(scenario_4=na_if(scenario_4,0.1)) %>% 
  left_join(afpop, by=c("iso3"= "country_code")) %>% 
  mutate(routine=.06,
         tot0=x2022/1.8+x2025/1.8+x2028/1.8+x2031/1.8+x2022*routine+x2023*routine+x2024*routine+x2025*routine+x2026*routine+x2027*routine+x2028*routine+x2029*routine+x2030*routine+x2031*routine+x2032*routine,
         tot2=x2022/1.8+x2023*(scenario_2/100)+x2024*(scenario_2/100)+x2025*(scenario_2/100)+x2026*(scenario_2/100)+x2027*(scenario_2/100)+x2028*(scenario_2/100)+x2029*(scenario_2/100)+x2030*(scenario_2/100)+x2031*(scenario_2/100)+x2032*(scenario_2/100),
         tot3=x2022/1.8+x2023*(scenario_3/100)+x2024*(scenario_3/100)+x2025/1.8+x2026*(scenario_3/100)+x2027*(scenario_3/100)+x2028/1.8+x2029*(scenario_3/100)+x2030*(scenario_3/100)+x2031/1.8+x2032*(scenario_3/100),
         tot4=x2022/scenario_4+x2025/scenario_4+x2028/scenario_4+x2031/scenario_4+x2022*routine+x2023*routine+x2024*routine+x2025*routine+x2026*routine+x2027*routine+x2028*routine+x2029*routine+x2030*routine+x2031*routine+x2032*routine,
         tot5=x2022/scenario_5+x2024/scenario_5+x2026/scenario_5+x2028/scenario_5+x2030/scenario_5+x2032/scenario_5+x2022*routine+x2023*routine+x2024*routine+x2025*routine+x2026*routine+x2027*routine+x2028*routine+x2029*routine+x2030*routine+x2031*routine+x2032*routine,
         s0vs2=tot2/tot0,
         s0vs3=tot3/tot0,
         s0vs4=tot4/tot0,
         s0vs5=tot5/tot0)
         # s2vs0=tot0/tot2,
         # s2vs3=tot3/tot2,
         # s2vs4=tot4/tot2,
         # s2vs5=tot5/tot2)


## Over 15-year time period - no huge differences, but it's common denominator for 3 and 2y campaigns.
# tnets15 <- table80rt %>% 
#   left_join(afpop) %>% 
#   mutate(routine=.06,
#          tot2=x2022/1.8+x2023*(scenario_2/100)+x2024*(scenario_2/100)+x2025*(scenario_2/100)+x2026*(scenario_2/100)+x2027*(scenario_2/100)+x2028*(scenario_2/100)+x2029*(scenario_2/100)+x2030*(scenario_2/100)+x2031*(scenario_2/100)+x2032*(scenario_2/100)+x2033*(scenario_2/100)+x2034*(scenario_2/100)+x2035*(scenario_2/100)+x2036*(scenario_2/100)+x2037*(scenario_2/100),
#          tot3=x2022/1.8+x2023*(scenario_3/100)+x2024*(scenario_3/100)+x2025/1.8+x2026*(scenario_3/100)+x2027*(scenario_3/100)+x2028/1.8+x2029*(scenario_3/100)+x2030*(scenario_3/100)+x2031/1.8+x2032*(scenario_3/100)+x2033*(scenario_3/100)+x2034/1.8+x2035*(scenario_3/100)+x2036*(scenario_3/100)+x2037/1.8,
#          tot4=x2022/scenario_4+x2025/scenario_4+x2028/scenario_4+x2031/scenario_4+x2034/scenario_4+x2037/scenario_4+x2022*routine+x2023*routine+x2024*routine+x2025*routine+x2026*routine+x2027*routine+x2028*routine+x2029*routine+x2030*routine+x2031*routine+x2032*routine+x2033*routine+x2034*routine+x2035*routine+x2036*routine+x2037*routine,
#          tot5=x2022/scenario_5+x2024/scenario_5+x2026/scenario_5+x2028/scenario_5+x2030/scenario_5+x2032/scenario_5+x2022+x2034/scenario_5+x2036/scenario_5+routine+x2023*routine+x2024*routine+x2025*routine+x2026*routine+x2027*routine+x2028*routine+x2029*routine+x2030*routine+x2031*routine+x2032*routine+x2033*routine+x2034*routine+x2035*routine+x2036*routine+x2037*routine,
#          s2vs3=tot3/tot2,
#          s2vs4=tot4/tot2,
#          s2vs5=tot5/tot2)

totalnets <- tnets %>% 
  select(iso3, lifespan, tot0, tot2, tot3, tot4, tot5) %>% 
  pivot_longer(contains("tot"), names_to = "scenario", names_prefix = "tot", values_to = "totalnets")

scenpct <- tnets %>% 
  select(iso_a2, iso3, lifespan, contains("s0vs")) %>% # s2vs0, s2vs3, s2vs4, s2vs5
  mutate(iso3=case_when(iso_a2=="ER" ~ "ERI",
                                TRUE ~ as.character(iso3))) %>% 
  mutate(s0vs0=1,
         code=iso3) %>% 
  pivot_longer(contains("s0"), names_to="scenario", names_prefix = "s0vs", values_to = "pct") %>% 
  mutate(iso2=countrycode(code, origin="iso3c", destination="iso2c")) %>% 
  mutate(name=countrycode(code, origin="iso3c", destination="country.name"))

avgscenpct <- scenpct %>% 
  group_by(scenario) %>% 
  summarize(mean=mean(pct, na.rm = TRUE)) 
```


```{r totalnets, dpi=300, fig.width=6, fig.cap="Total nets needed over 10 years, relative to full scale continuous distribution"}

mapscen <- scenpct %>%
  # filter(name!="Eritrea") %>%
  ggplot(aes(x = scenario, y = pct, fill = scenario)) +
  geom_col() +
  # geom_hline(yintercept = 0) +
  # scale_y_continuous(name = "Percent",
  #                    breaks = seq(-1, 1, 0.25),
  #                    labels = seq(-1, 1, 0.25)) +
  scale_x_discrete(labels = c("", "", "", "","")) +
  scale_y_continuous(labels = scales::percent) +
  facet_geo( ~ code, grid = ssa_grid, label = "code") +
  labs(title = "Percentage difference in total nets needed over 10 years\nto maintain ≥80% ITN access, relative to Status Quo\n(3 year campaigns quantified using population/1.8, with ANC/EPI ITNs)",
       x = "",
       y = "Percent",
       fill = "Scenario") +
  scale_fill_brewer(
    palette = "Dark2",
    labels = c(
      "Status Quo", 
      "Full Scale CD",
      "Campaigns + CD",
      "3-year Campaigns",
      "2-year Campaigns"
    )
  ) +
  theme_void() +
  theme(
    # legend.position="none",
    # axis.text.x = element_text(angle=45, hjust=1)
    # axis.text.x = element_blank(),
    axis.line = element_blank(),
    axis.line.x = element_blank(),
    axis.line.x.bottom=element_line(color="white"),
    axis.ticks.x = element_blank(),
    # axis.ticks.y = element_blank(),
    axis.text = element_text(size = 5),
    # panel.grid.major.x = element_line(color = "darkgrey", size = 0),
    strip.text.x = element_text(size = 6),
    strip.background = element_rect(color = "white", size = .5),
    legend.key.size = unit(.25, 'cm'),
    #change legend key size
    # legend.key.height = unit(1, 'cm'), #change legend key height
    # legend.key.width = unit(1, 'cm'), #change legend key width
    legend.title = element_text(size = 10),  #change legend title font size
    legend.text = element_text(size = 8), #change legend text font size)
    # axis.text.y = element_blank(),
    # axis.ticks = element_blank(),
    axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # legend.position="none",
    panel.background = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    plot.background = element_blank()
  )

asp <- avgscenpct %>% 
  ggplot(aes(x=scenario, y=mean, fill=scenario, label=scales::percent(round(mean, digits=2)))) +
  geom_col() +
  scale_fill_brewer(
    palette="Dark2",
    labels=c("Status Quo", "Full Scale CD", "Campaigns + CD", "3-year Campaigns", "2-year Campaigns")) +
  scale_x_discrete(labels=c("","","","","")) +
  scale_y_continuous(labels = scales::percent, breaks=c(0,1,2), limits=c(0,3)) + ## 
  geom_text(hjust=.5, vjust=-.75, size=2)+
  labs(fill="Scenario",
       y="",
       x="",
       title="Across all countries",
       # title="Percentage difference in total nets needed - mean of all countries"
       ) +
  theme(axis.ticks.x = element_blank(),
        legend.key.size = unit(.25, 'cm'), #change legend key size
        # legend.key.height = unit(1, 'cm'), #change legend key height
        # legend.key.width = unit(1, 'cm'), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=8),  #change legend text font size
        plot.margin = unit(c(.3,0,0,0), "cm"),
        rect = element_rect(fill = "white"),
        legend.position="none",
        plot.title = element_text(hjust = 0.8))




TotNets <- mapscen + inset_element(asp, left = -0.05, bottom = -0.09, right = .3, top = .3)+ 
  plot_annotation(tag_levels = 'A')
TotNets

```

## Are there enough primary school children to make school distribution feasible?


```{r schoolmappingdata}
africa = world %>%
  filter(continent == "Africa",!is.na(iso_a2)) 

sch <-  africa %>%
    left_join(schv2, by = "name_long") %>%
    st_transform("+proj=aea +lat_1=20 +lat_2=-23 +lat_0=0 +lon_0=25")

# then join with school dataset on iso_a2 NATIONAL LEVEL
sch <- sch %>% 
  left_join(qt, by = "iso_a2") %>% 
  mutate(feasible80 = if_else(currentprim > s280,"yes","no"),
         feasible70 = if_else(currentprim > s270, "yes","no"))

# then join with school dataset on iso_a2 REGIONAL LEVEL
allschq <- allsch %>% 
  left_join(qt, by = "iso_a2") %>% 
  mutate(feasible80 = if_else(percent_population_that_are_current_primary_students > s280,"yes","no"),
         feasible70 = if_else(percent_population_that_are_current_primary_students > s270, "yes","no")) %>% 
  drop_na(s270)

# summarize % of regions that are feasible for school dist at 70 and 80% targets (collapse)
pctregsch <- allschq %>% 
  group_by(iso_a2) %>%
  summarize(feas80=sum(feasible80=="yes"), feas70=sum(feasible70=="yes"), n=n()) %>%
  mutate(pct70=feas70/n,
         pct80=feas80/n) 

# join the africa shapefile with the regional percent df:
regsch <- africa %>% 
  left_join(pctregsch, by="iso_a2") %>% 
  st_transform("+proj=aea +lat_1=20 +lat_2=-23 +lat_0=0 +lon_0=25")
```

```{r schfunnat}
schfunnat <- function(column) {
  column <- sym(column) 
  
  ggplot(sch) +
  geom_sf(
    data = sch,
    aes(fill = as.factor(!!column)),
    color = "white",
    size = 0.5
  ) +
  theme_void() +
  scale_fill_brewer(palette = "Set2",
                   na.value = "WhiteSmoke",
                   direction = -1) +
  coord_sf() +
  labs(fill = "",
       title = "") +
  theme(plot.margin = grid::unit(c(0, 0, 0, 0), "null"))
}
```


```{r natschoolmaps}
sch1 <- schfunnat("feasible70") +
labs(fill = "",
       title = "Feasibility of Annual Primary School \nDistribution to achieve 70% ITN access \nin Scenario 2") 

sch2 <- schfunnat("feasible80") +
labs(fill = "",
       title = "Feasibility of Annual Primary School \nDistribution to achieve 80% ITN access \nin Scenario 2") 
```

```{r schfunreg}
schfunreg <- function(column) {
  column <- sym(column) 
  
  ggplot(regsch) +
  geom_sf(
    data = regsch,
    aes(fill = !!column),
    color = "white",
    size = 0.5
  ) +
  theme_void() +
    scale_fill_fermenter(n.breaks=6,
                         palette="PRGn",
                         # type="div",
                         direction=1,
                         na.value = "Linen",
                         labels = percent
                         ) +
  # scale_fill_steps(low="maroon", high="darkgreen",
  #                  na.value = "WhiteSmoke",
  #                  n.breaks = 6
  #                  ) +
  coord_sf() +
  labs(fill = "",
       title = "") +
  theme(plot.margin = grid::unit(c(0, 0, 0, 0), "null"))
}
```

```{r hhreachsch}
natlhh <-  africa %>%
    left_join(natl) %>%
    st_transform("+proj=aea +lat_1=20 +lat_2=-23 +lat_0=0 +lon_0=25")

schreach <- natlhh %>%   
  ggplot() +
  geom_sf(
    aes(fill = percent_hh_with_child_attending_primary_school),
    color = "white",
    size = 0.5
  ) +
  theme_void() +
    scale_fill_fermenter(n.breaks=5,
                         palette="Blues",
                         # type="div",
                         direction=1,
                         na.value = "WhiteSmoke") +
  # scale_fill_steps(low="maroon", high="darkgreen",
  #                  na.value = "WhiteSmoke",
  #                  n.breaks = 6
  #                  ) +
  coord_sf() +
  labs(fill = "",
       title = "Percent of households with any \nchild attending primary school") +
  theme(plot.margin = grid::unit(c(0, 0, 0, 0), "null"),
        plot.title = element_text(size=12))

cdreach <- natlhh %>%   
  ggplot() +
  geom_sf(
    aes(fill = percent_hh_with_any_pw_u1_or_school),
    color = "white",
    size = 0.5
  ) +
  theme_void() +
    scale_fill_fermenter(n.breaks=5,
                         palette="Greens",
                         # type="div",
                         direction=1,
                         na.value = "WhiteSmoke") +
  # scale_fill_steps(low="maroon", high="darkgreen",
  #                  na.value = "WhiteSmoke",
  #                  n.breaks = 6
  #                  ) +
  coord_sf() +
  labs(fill = "",
       title = "Percent households with any \ninfant under one year, \npregnant woman, or child attending \nprimary school") +
  theme(plot.margin = grid::unit(c(0, 0, 0, 0), "null"),
        plot.title = element_text(size=12))

natreach <- ggarrange(schreach, cdreach, labels="AUTO", align="hv")
```

```{r regschoolmaps}
schr1 <- schfunreg("pct70") +
labs(fill = "",
       title = "Percent of regions with sufficient \nprimary school enrollment \nto achieve 70% ITN access \nin Scenario 2") 
 

schr2 <- schfunreg("pct80") +
labs(fill = "",
       title = "Percent of regions with sufficient \nprimary school enrollment \nto achieve 80% ITN access \nin Scenario 2") 
```


```{r fig-school, fig.width = 10, fig.cap = "Percentage of regions/provinces per country where large-scale annual school distribution to achieve ITN access targets for A) 70% and B) 80% is feasible, assuming one ITN is given per child."}

# ggarrange(schr1, schr2, align="h", labels= "AUTO", legend="bottom", common.legend = TRUE, vjust=1, hjust=-.1)
# ggarrange(sch1, sch2, align="h", labels = "AUTO", legend="bottom", common.legend = TRUE, vjust=1.5, hjust=0.05)

combined <- schr1 + schr2 & theme(legend.position = "right")
combined + plot_layout(guides = "collect") + plot_annotation(tag_levels = 'A')
```

:::

The proportion of regions/provinces within each country where primary school students attending school met or exceeded the population quantifier are shown in Fig. \@ref(fig:fig-school), as an indication of the extent within a country where annual school distribution would be feasible. This assumes that only one ITN is given per pupil; for the countries in Fig. \@ref(fig:fig-school) with a limited proportion of regions where the primary-school-attending population is large enough, giving more than 1 ITN per pupil could provide a solution. Alternately, additional community-based channels could be designed to distribute ITNs alongside school-based distribution. 

:::

## Which strategies offer the most value for money?

```{r readpyp}
pyp <- read_dta("output/totalnetspyp.dta") %>% 
  clean_names() %>% 
  mutate(bestlabel=case_when(group==4 ~ paste0("pop/",round((scenario-400)/10, digits=1), " \nevery 3 years"),
                             group==5 ~ paste0("pop/",round((scenario-500)/10, digits=1), " \nevery 2 years"),
                             group==6 ~ "pop/1.8 \nevery 2 years",
                             group==1 ~ paste0("RCH at \npop x ",(scenario-100),"%"),
                             group==2 ~ paste0("annual CD \nat pop x ",(scenario-200),"%"),
                             group==3 ~ paste0("CD between campaigns \nat pop x ",(scenario-300),"%"),
                             TRUE ~ "")) %>% 
  mutate(bestlabel=case_when(bestlabel=="pop/1 every 2 years" ~ "pop/1.0 \nevery 2 years",
                             bestlabel=="pop/2 every 2 years" ~ "pop/2.0 \nevery 2 years",
                             bestlabel=="pop/1 every 3 years" ~ "pop/1.0 \nevery 3 years",
                             bestlabel=="pop/2 every 3 years" ~ "pop/2.0 \nevery 3 years",
                             TRUE ~ as.character(bestlabel)),
         wrap_lbl = stringr::str_wrap(bestlabel, width = 25),
         iso_a2=countrycode(iso3, origin = "iso3c", destination="iso2c")) %>% 
  left_join(rettimes)

```


```{r pyp, fig.width=10, fig.cap = "Frontier plots of person-years of ITN access vs total nets delivered, in illustrative populations of 10 million people for comparability"}

# hjust=-.2, vjust=.5, max.overlaps=10, 

pypfunction <- function(iso3) {
 # ptitle <- paste0("p",{{iso3}})
lifespan <- pyp %>% 
   filter(iso3 == {{iso3}}) %>% 
  summarize(lf=mean(lifespan)) %>% 
  pull()
  
            
pyp %>%
  filter(iso3 == {{iso3}}, best==1) %>%
  ggplot(aes(
    x = pyp / 1000000,
    y = totalnets / 1000000,
    color = as.factor(group),
    # alpha = as.factor(best)
  )) +
  geom_point() +
  # theme(legend.position = c(1.25, 0.8),
    # theme(legend.position = c(.3, .8)) +
        # plot.margin = unit(c(0.1, 5, 0.1, 0.1), "cm")) +
  geom_text_repel(aes(label = ifelse(best == 1, bestlabel, "")), max.overlaps=10, hjust=0, size=2.5) + #  force=3, xlim = c(0, 300)
    # geom_text(aes(label = ifelse(best == 1, bestlabel, "")), size=2.5, fontface="bold", hjust=-.1, vjust=-.2) +
  scale_color_brewer(
    palette = "Dark2",
    labels = c(
      "Status Quo",
      "Full scale CD",
      "Campaigns + CD",
      "3-year campaigns",
      "2-year campaigns",
      "2-year campaigns (pop/1.8)"
    )
  ) +
  labs(x = "",
       y = "",
       color = "",
       title = paste0(lifespan," years median retention time")) +
       # title = {{iso3}}) +
  # labs(x = "Person-years of ITN access (millions)",
  #      y = "Total nets delivered (millions)",
  #      color = "Scenario",
  #      title = {{iso3}}) +
  scale_alpha_manual(values = c(.3, 1)) +
    scale_x_continuous(limits=c(100,250)) +
  # coord_cartesian(clip = 'off') +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 9),
    title = element_text(size=10)
  ) +
  guides(alpha = "none", 
         color = guide_legend(override.aes = aes(label = ""))) ## remove the "a" from the marker in legend
}

p1 <- pypfunction("LBR")
p3 <- pypfunction("TZA")
p6 <- pypfunction("CMR")
p5 <- pypfunction("COG")
p4 <- pypfunction("TGO")
p2 <- pypfunction("GIN")



## save the legend separately, then remove legend from LB and TZ:
leg <- get_legend(p1) 

p1 <- p1 + theme(legend.position = "none")
p2 <- p2 + theme(legend.position = "none")
p3 <- p3 +theme(legend.position = "none")
p4 <- p4 + theme(legend.position = "none")
p5 <- p5 + theme(legend.position = "none")
p6 <- p6 + theme(legend.position = "none")

plots <- list(p1, p2, p3, p4, p5, p6)
main <- wrap_plots(plots, ncol=2) ## put the main plots into its own grob

main3 <- wrap_plots(p1, p3, p6, leg, ncol=2)
## Make a y-axis and x-axis label to be used across the mains as separate grobs:
p_ylab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Total nets delivered (millions)", angle = 90) +
  coord_cartesian(clip = "off")+
  theme_void()

p_xlab <- 
  ggplot() + 
  annotate(geom = "text", x = 1, y = 1, label = "Person-years of ITN access (millions)", angle = 0) +
  coord_cartesian(clip = "off")+
  theme_void()


## wrap the ylabel plot, main plots, a spacer, and the xlabel plot, setting the widths and heights for the whole set of 4:
# wrap_plots(p_ylab, main, plot_spacer(), p_xlab, nrow=2) +
#   plot_layout(widths = c(.1, 1), heights=c(1,.1))

## Now with only 3 countries:
# wrap_plots(p_ylab, main3, plot_spacer(), p_xlab, nrow=2) +
#   plot_layout(widths = c(.1, 1), heights=c(1,.1))

p1 <- p1 +
  labs(y="Total nets delivered (millions)",
       # x="")
       x="Person-years of ITN access (millions)")
p5 <- p5 +
  labs(x="Person-years of ITN access (millions)")

(p1 | p5) / leg +
  plot_layout(heights=c(1,.2))

# (p1 / p5 / leg) +
#   plot_layout(heights=c(1,1,.25))

ggsave("figs/Fig_pyp.png", height=5, width=6, dpi=300)
```

Frontier plots for all countries are included in Supplemental File 2.

# Discussion

## Takeaways (1)

1. Current status quo of conducting mass campaigns every three years using a population/1.8 quantifier is insufficient to achieve targets of 80% population access to ITNs in the majority of malaria-endemic countries, given overall retention times are estimated at below three years. 

1. Two year campaigns, however intuitive, ultimately require far more ITNs to maintain 80% population ITN access than under a strategy of continuous distribution. 
     a. Compared to the current status quo, full scale continuous distribution of nets could provide continuous ITN access at 80% or higher, for `r round((avgscenpct$mean[2]-1)*100, digits=0)`% more nets, while a strategy of 2-year mass campaigns using a quantification factor tailored for net retention rates would require `r round((avgscenpct$mean[5]-1)*100, digits=0)`% more nets than status quo with similar coverage outcomes. 

## Takeaways (2)

1. Population/1.8 does not fit all settings
    a. Net retention time is the major driving factor behind the calculations for the optimal quantification factor. 
    a. Countries with retention times of less than 2 years could not maintain ITN access at 80% between campaigns even when one ITN per person was delivered in the model, and countries with retention time of around 2.5 years required population/1.5 or population/1.2 to offset the rapid loss of nets post-campaign and still maintain sufficient ITN coverage. 
    a. However, even these approaches would introduce what most planners and donors would consider a vast "oversupply" of ITNs at each campaign.

1. Optimal quantification factors and the total number of nets that would be required can facilitate decision making for national programmes and their partners. 

## Implications

- The challenges of delivering more ITNs are clear - funding for both the nets and their distribution costs; donor appetite; not to mention the additional cost of new types of ITNs recommended for areas with insecticide resistance. 
- The costs of continuing to deliver insufficient quantities of ITNs and provide only intermittent protection are also clear - continued loss of life, educational achievement, quality of life due to malaria. 

## What about making nets last longer?

- Improvements in both areas would contribute substantially towards increasing retention times, but it is unlikely that this would offset the general and continued challenges of keeping nets in good condition for long periods of time across settings in malaria-endemic areas. Net durability is driven by behavioral factors in part, but also the household environment, which in many settings is simply a difficult place for nets to survive. 
- This is particularly true for people living through humanitarian emergencies, and this population is projected to increase due to climate change and climate-related emergencies. 

## How accurate are the retention times used in the analysis?

- All of these results hinge on the estimated retention times. 
- It's important to highlight that ITN durability studies, while largely in line with retention times used in this paper, do diverge in several cases. 
    - Most notably, Liberia's retention time was estimated at 1.0 years, but an ITN durability study completed in 2021 in two counties observed a median survival in serviceable condition of 4 years. 
    - Durability have been demonstrated to vary subnationally; durability monitoring of ITNs in northern Nigeria showed they median lifespans of over five years, while the same product monitored simultaneously in southern zones of Nigeria had a lifespan of just over three years [@Obi:2020eza], consistent with findings from an earlier cross-sectional durability study in similar areas of Nigeria [@Kilian:2015hk]. 
    - Programmes must consider potential differences in net retention behavior and net durability as they weigh their quantification decisions.

## Are countries currently doing CD doing enough?

1. Ghana distributes ITNs to school children in grades 2 and 6 between 3-year campaigns, while Tanzania has implemented full scale school distribution in 14 mainland regions since 2016, and expanded the programme to 5 additional regions in 2022. 
2. The quantities of ITNs distributed to school children in Ghana amount to `r round(1400000/with(afpop, x2020[which(country_name=="Ghana")])*100, digits=1)`% of the population (1.4 million ITNs in the [2020 school distribution](https://allianceformalariaprevention.com/wp-content/uploads/2021/06/CD_Ghana_SBD_Case_Study_0620201.pdf)) - far from the `r with(table80, scenario_3[which(name == "Ghana")])`% estimated to be needed to maintain ITN access at levels of 80%. 
3. Tanzania's school net programme has delivered ITNs equivalent to 12-16% of the population in SNP zones over recent years, but they may require quantification of population x `r with(table80, scenario_2[which(name == "Tanzania")])`% to maintain ITN access at 80%, discussed in more detail elsewhere [@10.1186/s12936-022-04272-w].

## Is school distribution the best option for full scale CD?

- School distribution, conducted annually to all or selected primary school classes, is a promising approach to delivering ITNs [@Koenker:2013ed; @10.1093/heapol/czab140; @Yukich:2020km; @10.1186/s12936-022-04272-w]. 
- Studies estimate that school-age children drive at least 60% of malaria transmission [@10.1186/s12936-018-2295-4; @10.4269/ajtmh.21-1263], due in part to their lower rates of ITN use, especially when households don't own enough nets [@Olapeju:2018bc; @10.4269/ajtmh.21-1263]. 
- Ensuring that these children - and their family members - are prioritized for protection with ITNs, along with vulnerable pregnant women and children, is a hallmark of the school distribution strategy. 
- Annualized distributions also facilitate planning, avoiding the 3-yearly overload of mass campaign planning among national malaria programmes and their implementing partners, and the platform leverages Ministry of Education personnel, providing opportunities for additional integration of other school health interventions.

## What about ITN use?

- This analysis uses a target of 80% population ITN access, but it must be noted that for ITN use levels to reach 80%, ITN access must be at least 90%, given the persistent (yet happily quite small) gap between ITN access and ITN use [@Koenker:2014gb;@10.1038/s41467-021-23707-7;@Bhatt:2015gn]. 
- Targeting ITN access at 80% will max out ITN use around 70% or lower. 
- Donors and programmes must therefore evaluate what target levels of ITN use are necessary for success, and adjust ITN access targets upwards accordingly.

## Limitations

1. Retention times for certain countries are based on a limited number of surveys, described further in [@10.1038/s41467-021-23707-7]. We account for the uncertainty of these estimates in the calculations of ITN access. 
2. Localized durability monitoring studies sometimes find significantly longer median survival of ITNs than the retention times estimates, which could indicate subnational differences in ITN longevity or be evidence of analytical challenges in the ITN retention times or conversely, Hawthorne effect in the durability monitoring studies. 
3. The relationship between nets-per-capita and ITN access is assumed to be consistent regardless of ITN distribution strategy, but it could be influenced by oversaturation of ITNs in certain types of households, as occurs with school distribution of ITNs. 
4. Retention behavior is influenced by net availability (or lack thereof); with increasing availability of nets, households could be disincentivized to take care of their nets for longer, if new nets are readily available. 

```{r}
# This is due essentially to a larger fraction of nets being unavailable for use where household size is smaller: e.g. 2 nets for 3 people leaves "half a net" unable to be used, whereas 6 nets for 10 people leaves 
```



## Conclusion

- Given variation in ITN retention times across countries, tailored quantification approaches for mass campaigns and continuous distribution strategies are warranted. 
- To reach target levels of ITN use of 80% of the population, ITN access must be maintained near 90% in most settings. 
- The quantity of ITNs required to meet these goals are substantially larger than current plans, but strategies with continuous/annual distributions are likely to provide higher ITN access with fewer nets than tailored universal coverage campaigns. 
- Strategies with continuous/annual distributions may also provide better ITN access with only 8% more ITNs needed than current status quo of 3-year campaigns quantified using population/1.8. 
- National programmes and their funding partners should work to increase the number of ITNs distributed to those vulnerable to malaria, while at the same time working to extend the useful life of these critical commodities.


## Availability of data and materials

- Code and complete tables/results for countries are available at https://github.com/hkoenker/Quantification.  



# Supplementary information

---

```{r s2s3tablelong, fig.width=10, tab.cap = "Recommended annual quantifiers for continuous distribution channels. All scenarios assume that ANC and EPI delivery of ITNs is ongoing and provides nets to 6% of the population. However, quantifiers listed in the table represent only the continuous distribution channel, e.g. Angola would require both ANC/EPI distribution as well as continuous distribution quantified using population x 27% to maintain ITN access at levels of 70%."}
tables2s3function(table_q_s2s3long)
```

---

```{r s4tablelong, fig.width=10, tab.cap = "Lowest level of ITN access between 3-year campaigns at different population quantifiers for all countries. Green color reflects higher ITN access while red indicates lower ITN access reached between campaigns.  Routine ITN delivery to pregnant women and infants is assumed."}
s4tablefunction(s4minrtlong)
```

---

```{r s5tablelong, fig.width=10, tab.cap = "Lowest level of ITN access between 2-year campaigns at different population quantifiers for all countries. Green color reflects higher ITN access while red indicates lower ITN access reached between campaigns. Values of 100 indicate excess nets in the system (for example Cameroon). Routine ITN delivery to pregnant women and infants is assumed."}
s5tablefunction(s5minrtlong)
```

---

```{r recctablelong, fig.width=10, tab.cap="Summary of recommended quantifiers for all countries and scenarios, to maintain ITN access at or above 80%. The quantifiers are for only the continuous distribution channel or mass campaign; annual RCH distribution equivalent to 6% of the population is assumed in each scenario, but is not part of the listed quantifiers"}
recctablefunction(table80rtlong)
```

---

```{r figreach, fig.width=10, fig.cap = "A) Percent of households with a child attending primary school; B) Percent of households with a pregnant woman, child under 12 months, or child attending primary school. Data from most recent Demographic and Health Survey"}
natreach
```

## Supplementary File 1

- Estimated ITN access under five ITN distributions scenarios and at varying quantification approaches (`r totalscenarios` iterations)

- [Link to file](https://github.com/hkoenker/Quantification/blob/master/04_Quant_Plots.html)

## Supplementary File 2 

- Frontier plots of Person-years of ITN access vs Total nets delivered for 40 countries

- [Link to file](https://github.com/hkoenker/Quantification/blob/master/07_SI_2_PYP.html)


## References


